Hypertension and microbiome

### 2019-01-02 rrbiome.Rmd
Minor typo

plot_maaslin_heatmap_final(maas.results.df.signf,
                      xlab.text="Genera",
                      beta.maxabs=max(abs(maas.results.df.signf[,'beta'])),
                      order.by.category=FALSE)
```

>>>>

plot_maaslin_heatmap_final(maas.results.df.signf,
                      xlab.text="Genera",
                      beta.maxabs=max(abs(maas.results.df.signf[,'Beta'])),
                      order.by.category=FALSE)
```
